---
title: "creditcard_ambm"
author: "Angela"
date: "5/9/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## business problem/goal

In this R project, I will present how to perform detention of credit card frauds, through the verious algortihms like desicion tree model, and logistics regrresion model. 

For carrying out the credit card fraud detection, I will make use of the Card Transactions dataset that contains a mix of fraud as well as non-fraudulent transactions.

The file has 56 observation of 8 variables, it was imported from a CSV file

## getting the data

```{r creditcard}
summary(creditcard)
```

##see first 6 rows of my data


```{r}
head(creditcard, 6)

```

##view and rename a column

##now rename V1 

```{r creditcard}
colnames(creditcard)[colnames(creditcard)=='V1']<-'1V'

colnames(creditcard)
```
##characteristics of my data

The creditcard data has `r ncol(creditcard)` rows and `r nrow(creditcard)`rows. Bellow is a summary of the types of variables in the dataset:


```{r creditcard}
str(creditcard)
```
##the characteristics tables

```{r}
text_tbl<-data.frame(names = c("Amount", "Class"), Description = c("this is the amount expend per transaccion", "this is the class identified per transaccion"))

#to print the table in my output:

print(text_tbl)
```
## ## Data exploration

```{r}
dim(creditcard)
tail(creditcard)
table(creditcard$Class)
summary(creditcard$Amount)
names(creditcard)
var(creditcard$Amount)
sd(creditcard$Amount)
```

## Data Manipulation
```{r}
head(creditcard)
creditcard$Amount=scale(creditcard$Amount)
newcreditcard=creditcard[,-c(1)]
head(newcreditcard)
```
##Data Modeling
```{r}
library(caTools)
set.seed(123)
data_sample= sample.split(newcreditcard$Class, SplitRatio = 0.80)
train_data= subset(newcreditcard, data_sample==TRUE)
test_data= subset(newcreditcard, data_sample==FALSE)
dim(train_data)
dim(test_data)
```
## decision tree model
```{r}
library(rpart)
install.packages("rpart.plot")
library(rpart.plot)
decisionTree_model <- rpart(Class ~ . , creditcard, method = 'class')
predicted_val <- predict(decisionTree_model, creditcard, type = 'class')
probability <- predict(decisionTree_model, creditcard, type = 'prob')
rpart.plot(decisionTree_model)
```

## Logistics regression model
```{r}
Logistic_Model=glm(Class~.,test_data,family=binomial())
summary(Logistic_Model)

plot(Logistic_Model)
```